Reduced plasticity and opportunity for selection in terrestrial ectotherm populations under climate change

### 2023-03-30 ms.qmd
Add in flextable

# Create the table
    tabs1 <- rbind(fixed, random)
   tabs1_2 <-  gt(tabs1) %>%  
    fmt_number(columns = 2:5, decimals = 2) %>% 
    tab_row_group(label = "Fixed Effects", rows = 1:7) %>% 
    tab_row_group(label = "Random Effects", rows = 8:11) %>%  
    tab_style(style = list(cell_text(weight = "bold")),
          locations = list(cells_column_labels(), cells_row_groups())) %>% 
    opt_table_lines(extent = "none")  %>% 
    tab_style(style = cell_borders(sides = c("top", "bottom")),
          locations = list(cells_column_labels()))  %>% 
    tab_style(style = cell_borders(sides = "bottom", weight = px(2)),
          locations =  cells_body(rows = 7))
    #tabs1_2

    flextable(tabs1)  %>%  autofit()
```

>>>>

# Create the table
    tabs1 <- rbind(fixed, random)

    flextable(tabs1)  %>%  add_body_row()  %>% autofit()
```
